### 2017-07-13 architecture.tex
Minor

\section{Architecture and Implementation}
\label{sec:architecture}

@@

Datasets come with various levels of sensitivity. Selecting the policies, protocols, infrastructure, and 
software settings to ensure to ensure that individual datasets are adequately secured requires
case-by-case consideration. To represent these policies, such that dataset owners can manage these considerations
we define safe-collections. Safe-collections enable system administrators to partition the key administration
aspects of managing the relationship between analysts (data users/accessors) and data. 
Safe-collections encapsulate a data-store where the dataset will reside, and a consistent set of policies
that controls access to the data-store as well the policies themselves.

Safe-collections offer a range of policies including specification of limits as well as management 
of access, usage, and data export. We define a meta-policy model via which administrators may define
the set of policies permissible on a safe-collection. Each safe-collection is associated with a steward
(or group of stewards) who may manage safe-collection policies. To simplify use, the meta policy schema 
is translated to a web-based form that can be completed by users during creation of a safe-collection. 
The completed form is stored as a set of special tags on the collection's data storage. The schema is enforced
by the various services that interact with the safe-collection. The schema and the generated form are shown in
\figurename~\ref{fig:schema}

\subsubsection{Policies}
Safe-collections are defined with policies that govern access to, and use of, 
data in that collection. The policies supported by safe-collections are as 
follows:

@@

% Public data
Public datasets are assumed to contain no sensitive content and thus do not require access control nor
export control. Setting \texttt{SecurityClass} to \texttt{Public} indicates that the safe-collection does
not require a Steward and that all authenticated users on \NAME may access this dataset. None of the added
security features of safe-collections need apply.

% Common features for private data
Confidential and regulated datasets both require \texttt{SecurityClass} to be set to \texttt{Private}
and require that a steward group is specified. In addition, constraints can be set on the duration
for which analysts could be granted access. This ensures that access privileges expire and require
re-evaluation of the scope and nature of the analyst's work before access is extended. To limit the risk of
re-identification in datasets that contain anonymized data the safe-collections allow for whitelisting and
blacklisting other safe-collections. Job submissions to \NAME are checked for data requests that have
linkage conflicts, and denied at submit time.
\yadu{Linkage feature pending}

% cite garfinkel for de-identification risks
Safe-collections that contain regulated datasets often require oversight to ensure that all computed results
are inspected and approved by a steward before export. This is enforced by setting the
\texttt{ExportStewardApprovalReqd} flag.
Analysis results from tasks that consumed data from any safe-collection with this flag has all of the
results posted back to the same safe-collection, thus inheriting the same privileges as the source.
% worker roles are granted write privileges to the outputs section of a safe-collection
As a result, only stewards can view the results and export to a public safe-collection. Since results are
stored within the parent safe-collection, users can apply analysis operations on results without oversight,
and only request for export of the final results of a deep analysis pipeline.

@@

% Why do we have them / inital role
As more data-sets with varying degrees of sensitivity are added to the \NAME platform it becomes a matter
of necessity to distribute key administrative privileges from the system administrator roles to the curators
of the data-set. Stewards play a leadership role in evaluating the disclosure risks associated with a
dataset and codifying the security protocols protecting the safe-collection.

% access
Analysts can list all available safe-collections and request access to ones that they require.
Stewards evaluate these requests and approve access for a duration. Approvals are implemented as an additional
policy added to the list of s3 bucket policies for the safe-collection. \NAME ensures that the policy
being added is consistent with the meta-policy for the safe-collection, for eg. expiration for the policy
must be within the duration specified in the \texttt{MaxApprovalDur}.
\yadu{pending}

% export
On export controlled safe-collections, results generated by analysis tasks on \NAME are not visible to the
analysts until approved by a Steward. This is implemented by having workers write all results to the
parent safe-collections output directory and thus inheriting the same security privileges of the parent.
On \NAME stewards have complete visibility over the set of inputs, and operations made by the analysts
in order to generate their results. It is also possible to trace the provenance of the results from an
analysis pipeline since all analysis tasks are logged.
Stewards export the results by transferring the results out of the safe-collection and onto a public
safe-collection from which analysts can view results. It is important to note that even public
safe-collections have server side encryption and are only accessible to authenticated users via temporary
signed urls.

@@

>>>>

\section{Safe Collection Model}
\label{sec:architecture}

@@

Datasets come with various levels of sensitivity. Selecting the policies, protocols, infrastructure, and 
software settings to ensure to ensure that individual datasets are adequately secured requires consideration
on a case-by-case basis. 
%To represent these policies, such that dataset owners can manage these considerations,
%we define safe-collections. 
Safe-collections enable system administrators to partition the key administration
aspects of managing the relationship between users (e.g., analysts) and data. 
Safe-collections encapsulate the data-store in which a dataset will reside, and a consistent set of policies
that controls access to the data-store.

Safe-collections are defined with policies that govern limits as well as access to, and use of, 
data in that collection. They specifically regulate access, usage, and data export.
The policies supported by safe-collections are as follows:

@@

%% Public data
%Public datasets are assumed to contain no sensitive content and thus do not require access control nor
%export control. Setting \texttt{SecurityClass} to \texttt{Public} indicates that the safe-collection does
%not require a Steward and that all authenticated users on \NAME may access this dataset. None of the added
%security features of safe-collections need apply.
%
%% Common features for private data
%Confidential and regulated datasets both require \texttt{SecurityClass} to be set to \texttt{Private}
%and require that a steward group is specified. In addition, constraints can be set on the duration
%for which analysts could be granted access. This ensures that access privileges expire and require
%re-evaluation of the scope and nature of the analyst's work before access is extended. To limit the risk of
%re-identification in datasets that contain anonymized data the safe-collections allow for whitelisting and
%blacklisting other safe-collections. Job submissions to \NAME are checked for data requests that have
%linkage conflicts, and denied at submit time.
%\yadu{Linkage feature pending}
%
%% cite garfinkel for de-identification risks
%Safe-collections that contain regulated datasets often require oversight to ensure that all computed results
%are inspected and approved by a steward before export. This is enforced by setting the
%\texttt{ExportStewardApprovalReqd} flag.
%Analysis results from tasks that consumed data from any safe-collection with this flag has all of the
%results posted back to the same safe-collection, thus inheriting the same privileges as the source.
%% worker roles are granted write privileges to the outputs section of a safe-collection
%As a result, only stewards can view the results and export to a public safe-collection. Since results are
%stored within the parent safe-collection, users can apply analysis operations on results without oversight,
%and only request for export of the final results of a deep analysis pipeline.

@@

% Why do we have them / inital role
As more datasets with varying degrees of sensitivity are added to the \NAME platform it becomes a matter
of necessity to distribute key administrative privileges from the system administrator roles to the curators
of the data-set. Stewards play a leadership role in evaluating the disclosure risks associated with a
dataset and codifying the security protocols protecting the safe-collection.

% access
Analysts can list all available safe-collections and request access to ones that they require.
Stewards evaluate these requests and approve access for a duration. Approvals are implemented as an additional
policy added to the list of s3 bucket policies for the safe-collection. \NAME ensures that the policy
being added is consistent with the meta-policy for the safe-collection, for example, expiration for the policy
must be within the duration specified in the \texttt{MaxApprovalDur}.

% export
On export controlled safe-collections, results generated by analysis tasks on \NAME are not visible to the
analysts until approved by a Steward. This is implemented by having workers write all results to the
parent safe-collections output directory and thus inheriting the same security privileges of the parent.
On \NAME stewards have complete visibility over the set of inputs, and operations made by the analysts
in order to generate their results. It is also possible to trace the provenance of the results from an
analysis pipeline since all analysis tasks are logged.
Stewards export the results by transferring the results out of the safe-collection and onto a public
safe-collection from which analysts can view results. It is important to note that even public
safe-collections have server side encryption and are only accessible to authenticated users via temporary
signed URLs.

@@

\section{Implementation}

We define a meta-policy model via which administrators may define
the set of policies permissible on a safe-collection. Each safe-collection is associated with a steward
(or group of stewards) who may manage safe-collection policies. To simplify use, the meta policy schema 
is translated to a web-based form that can be completed by users during creation of a safe-collection. 
The completed form is stored as a set of special tags on the collection's data storage. The schema is enforced
by the various services that interact with the safe-collection. The schema and the generated form are shown in
\figurename~\ref{fig:schema}
